Summarize twas: chr17 to 22

### 2020-08-14 analysis/simulation-multi-ukbchr17to22-gtex.adipose.Rmd
susieI

```{r rpip 1, fig.height=4, fig.width=10}
chrom = 18
f <- get_files(tag= "20200721-1-2" , tag2 = tag2s[1])
allchr <- read.table(f[["rpip"]], header = T)
a <- allchr[allchr["chrom"]==chrom,]
print(paste("plot for chr", chrom))
par(mar=c(5, 4, 4, 6) + 0.1)
with(a, plot(p0, rPIP, col ='salmon', xlab = "position", ylab= "Sum of PIP", type = 'h', lwd = 2))
par(new = T)
with(a, plot(p0, nCausal, pch =19, col = "darkgreen",axes = FALSE, bty = "n", xlab = "", ylab = ""))
axis(side = 4)
mtext(side = 4, line = 3, 'No. causal signals')
legend("topleft",
       legend=c("Mr.ASH PIP", "# Causal"),
       lty=c(1,0), pch=c(NA, 19), col=c("salmon", "darkgreen"))
grid()
```

>>>>

```{r rpip 1, fig.height=4, fig.width=10}
chrom = 17
f <- get_files(tag= "20200721-1-1" , tag2 = tag2s[1])
allchr <- read.table(f[["rpip"]], header = T)
a <- allchr[allchr["chrom"]==chrom,]
print(paste("plot for chr", chrom))
par(mar=c(5, 4, 4, 6) + 0.1)
with(a, plot(p0, rPIP, col ='salmon', xlab = "position", ylab= "Sum of PIP", type = 'h', lwd = 2))
par(new = T)
with(a, plot(p0, nCausal, pch =19, col = "darkgreen",axes = FALSE, bty = "n", xlab = "", ylab = ""))
axis(side = 4)
mtext(side = 4, line = 3, 'No. causal signals')
legend("topleft",
       legend=c("Mr.ASH PIP", "# Causal"),
       lty=c(1,0), pch=c(NA, 19), col=c("salmon", "darkgreen"))
grid()
```

### 2020-08-14 analysis/simulation-multi-ukbchr17to22-gtex.adipose_sa2_v2.Rmd
susie names
susieI

```{r rpip 1, fig.height=4, fig.width=10}
chrom = 18
f <- get_files(tag= "20200721-1-3" , tag2 = tag2s[1])
allchr <- read.table(f[["rpip"]], header = T)
a <- allchr[allchr["chrom"]==chrom,]
print(paste("plot for chr", chrom))
par(mar=c(5, 4, 4, 6) + 0.1)
with(a, plot(p0, rPIP, col ='salmon', xlab = "position", ylab= "Sum of PIP", type = 'h', lwd = 2))
par(new = T)
with(a, plot(p0, nCausal, pch =19, col = "darkgreen",axes = FALSE, bty = "n", xlab = "", ylab = ""))
axis(side = 4)
mtext(side = 4, line = 3, 'No. causal signals')
legend("topleft",
       legend=c("Mr.ASH PIP", "# Causal"),
       lty=c(1,0), pch=c(NA, 19), col=c("salmon", "darkgreen"))
grid()
```

>>>>

```{r rpip 1, fig.height=4, fig.width=10}
chrom = 18
allchr <- read.table(, header = T)
a <- allchr[allchr["chrom"]==chrom,]
print(paste("plot for chr", chrom))
par(mar=c(5, 4, 4, 6) + 0.1)
with(a, plot(p0, rPIP, col ='salmon', xlab = "position", ylab= "Sum of PIP", type = 'h', lwd = 2))
par(new = T)
with(a, plot(p0, nCausal, pch =19, col = "darkgreen",axes = FALSE, bty = "n", xlab = "", ylab = ""))
axis(side = 4)
mtext(side = 4, line = 3, 'No. causal signals')
legend("topleft",
       legend=c("Mr.ASH PIP", "# Causal"),
       lty=c(1,0), pch=c(NA, 19), col=c("salmon", "darkgreen"))
grid()
```
